Efficient pedigree recording for fast population genetics simulation

### 2017-11-18 forwards_paper.tex
Very rough outline of Alg W using table notation.
closes #24

\begin{taocpalg}{W}{Forwards-time tree sequence}
{Simulates a randomly mating population $P$ of $N$ haploid individuals,
with a probability of death per generation $\delta$ and a chromosome of length
$L$ for $T$ generations. On termination, there will be $n$ nodes with times recorded
in the vector $\tau$, and $E$ will contain a set of $(\ell, r, p, c)$ tuples
describing the recorded edges.
}

\algstep{W1.}{Initialisation.}{
 For $0 \leq j < N$, set $P_j \leftarrow j$ and $\tau_j \leftarrow T$.
Set $E\leftarrow \emptyset$, $t \leftarrow T$ and $n \leftarrow N$.
}

@@

\algstep{W4.}{Mortality.}{ If $\randomuniform([0, 1)) \geq \delta$ go to \algref{W9}.
}

\algstep{W5.}{New node.}{Set $P'_j \leftarrow n$ and $\tau_n \leftarrow t$.
}

@@

\algstep{W7.}{Record edges}{Set 
    $E \leftarrow E \cup \left\{ (0, x, P_a, n), (x, L, P_b, n) \right\}$.
}

\algstep{W8.}{Increment the current node.}{
$n \leftarrow n + 1$.
}

\algstep{W9.}{Loop tail}{Set $j \leftarrow j + 1$ and go to \algref{W3}.
}

>>>>

\begin{taocpalg}{W}{Forwards-time tree sequence}
{Simulates a randomly mating population $P$ of $N$ haploid individuals,
with a probability of death per generation $\delta$ and a chromosome of length
$L$ for $T$ generations. Events are recorded in a node table $\mathcal{N}$
and edge table $\mathcal{E}$. Simplify is run every $s$ generations.
}

\algstep{W1.}{Initialisation.}{
Set $\mathcal{N} \leftarrow \mbox{NodeTable}()$ and $\mathcal{E}
\leftarrow \mbox{EdgeTable}()$ and $t \leftarrow T$.
 For $0 \leq j < N$, set $P_j \leftarrow \mbox{add}(\mathcal{N}, T)$.
}

@@

\algstep{W4.}{Mortality.}{ If $\randomuniform([0, 1)) \geq \delta$ go to \algref{W8}.
}

\algstep{W5.}{New node.}{Set $u \leftarrow \mbox{add}(\mathcal{N}, t)$ and $P'_j \leftarrow u$.
}

@@

\algstep{W7.}{Record edges}{
Call $\mbox{add}(\mathcal{E}, (0, x, P_a, u))$ and $\mbox{add}(\mathcal{E}, (x,
L, P_b, u))$.
}

\algstep{W8.}{Loop tail}{Set $j \leftarrow j + 1$ and go to \algref{W3}.
}

\algstep{W9.}{Simplify}{TODO}
